---
title "Exploring Flowcharts using DiagrammeR - Hello World"
author: "Rebecca Handcock"
date: "2023-05-07"
output: html_document
---


```{r warning=FALSE, message=FALSE, include=FALSE}
#------------------------------------------------|
# setup packages
#------------------------------------------------|

# Github: https://github.com/rich-iannone/DiagrammeR
# Functions: https://rich-iannone.github.io/DiagrammeR/reference/index.html

# DiagrammeR is a package within htmlwidgets for R. It is used to generate graphs using graphviz and mermaid library.
#install.packages("DiagrammeR")
library(DiagrammeR)

# rsvg: Renders vector-based svg images into images
library(rsvg)

# Connect to Bigquery
library(bigrquery)
library(DBI)

# helpful libraries
library(stringr)
library(dplyr)
library(purrr)

```


```{r message=FALSE, warning=FALSE}
#------------------------------------------------|
# FUNCTION export grViz graph to an image file
#------------------------------------------------|

F_export_grViz_graph2image <- function(graph2plot){
  # 1. Process the graph
  tmp = DiagrammeR::grViz(graph2plot)

  # 2. Convert to SVG, then save as png
  tmp = DiagrammeRsvg::export_svg(tmp)
  tmp = charToRaw(tmp) # flatten
  filename <- paste(deparse(substitute(graph2plot)), ".png", sep = "")
  print(filename)
  rsvg::rsvg_png(tmp, filename) # saved graph as png in current working directory
  }
```


#------------------------------------------------|
# Connect to BigQuery database
#------------------------------------------------|

```{r Test graph}
# METHOD 1: Simple graph with default all-in-one creation of the graph

test_var = "Hi there!"

graph_test <- "digraph {
  graph[layout = dot, rankdir = LR]
  
  a [label = 'Test label @@1']
  b [label = '@@2']
  c
  
  a -> b -> c 
  }
    # ------ Add footnotes 
    [1]:'Hello!'
    [2]: test_var
  "

F_export_grViz_graph2image(graph_test)
```

# --------------------------------------
# METHOD 2: Creating the graph from a DOT file, e.g. dot-graph.gv
### HOW TO RANK rank=same {NODE_Imported_dois, DATA_AcademicObservatory}
### HOW TO LABEL LINES DATA_AcademicObservatory -> P1_Combined_AO_and_Contributed[label = ' @@2 DOIs']
### HOW TO HAVE FOLDERS: data2 [label = 'Dataset 2', shape = folder, fillcolor = Beige]
### HOW TO Include a quote in a label, e.g.   \\' 
### HOW TO:   A cluster is a subgraph placed in its own distinct rectangle of the layout. A subgraph is recognized as a cluster ### when its name has the prefix cluster
### subgraph cluster_A {
### AAAA [label = 'Testing AAA']
### BBBB
#   https://graphviz.org/doc/info/shapes.html


